---
title: "Photographer Feedback History Cluster Second-level RSA Visualization"
output: 
  github_document:
    toc: true
    toc_depth: 3
---

## Goal

- Visualization of second-level RSA results using exploration models
  - Exploration Time, Exploration Distance, Capture Distance models
  - No partial correlation

- Visualization of partial correlation-based RSA results
  - (1) Feedback history models (Recent-2 or Recent-3 Trial) controlling for the Capture Distance model
  - (2) Capture Distance model controlling for either Recent-2 or Recent-3 Trial model
  
## Notes

- MiOG/IFG Feedback History clusters
  - See `second-level/output/cross_validated_cluster_mask/recent_2_and_recent_3_trial`

- Second-level RSA results are from `second-level/output/second_level_rsa`


## Load libraries

```{r}
knitr::opts_chunk$set(dpi = 300)

library(tidyverse)
library(easystats)
library(ggforce)
library(ggnewscale)
library(rstatix)
library(ggpubr)
library(lmerTest)
library(broom.mixed)
library(AICcmodavg)
library(emmeans)
library(glue)
library(slider)
```

```{r}
# Define a global theme for visualization
global_theme <- theme(
    legend.position = "none",
    plot.title = element_text(size = 25, hjust = 0.3),
    axis.title = element_text(size = 18),
    axis.text = element_text(size = 15),
    strip.text = element_text(size = 18),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(linewidth = 1, lineend = 'square'),
    axis.ticks = element_line(linewidth = 1),
    strip.background = element_blank(),
    panel.background = element_blank(),
  )
```


## Second-level RSA: Exploration models

```{r}
# Helper function for visualization
# `limits`, `breaks` paramters define the x axis of the figure
# `exploration_sigs` define significant model names from the second-level RSA
plot_second_level_RSA_exploration <- function(data_df, limits, breaks, exploration_sigs) {
  long_df <- data_df %>%
    pivot_longer(exploration_time:capture_distance,
                 names_to = "model",
                 values_to = "correlation") %>%
    mutate(significant = case_when(
      model %in% exploration_sigs ~ "exploration",
      .default = "ns",
    )) %>%
  mutate(
    model = case_match(
      model,
      "exploration_time" ~ "Exploration Time",
      "exploration_distance" ~ "Exploration Distance",
      "capture_distance" ~ "Capture Distance",
    )
  ) %>%
  mutate(model = factor(
    model,
    levels = c(
      "Exploration Time",
      "Exploration Distance",
      "Capture Distance"
    ))
  )
  
  long_df %>%
    ggplot(aes(x = forcats::fct_rev(model), y = correlation)) +
    geom_hline(yintercept = 0.0, linetype = "dashed") +
    stat_summary(geom = "linerange", fun.data = "mean_cl_boot", fun.args = list(B = 10000), color = '#636363', alpha = 0.3, linewidth = 13) +
    stat_summary(geom = "crossbar", fun = mean, fun.min = mean, fun.max = mean, width = 0.37, linewidth = 0.8, color = 'black') +
    geom_jitter(aes(color = significant), size = 2, alpha = 0.5, width = 0.15, height = 0) +
    coord_flip() +
    labs(x = "", y = "RSA Correlation (Z-scored)") +
    scale_color_manual(values = c('ns' = '#bdbdbd', 'feedback' = '#3182bd', 'exploration' = '#31a354')) +
    scale_y_continuous(breaks = breaks, limits = limits) +
    theme_bw() +
    global_theme +
    theme(axis.text.y = element_text(hjust = 0))
}
```

### MiOG cluster

#### Discovery group

```{r}
discovery_MiOG_exploration_df <- read_csv(
  "./data/second_level_rsa/exploration_second_level/discovery_MiOG_second_level.csv",
  col_types = cols(
    subgroup = col_factor(),
    subject_id = col_factor(),
    cluster = col_factor(),
    exploration_time = col_double(),
    exploration_distance = col_double(),
    capture_distance = col_double(),
  )
)
```

```{r fig.height=4, fig.width=8}
plot_second_level_RSA_exploration(discovery_MiOG_exploration_df, limits = c(-0.35, 0.6), breaks = c(-0.3, 0, 0.3, 0.6), exploration_sigs = c("capture_distance"))
```

```{r}
ggsave("./output/second_level_rsa/exploration_second_level/discovery_MiOG_exploration.png", height = 4, width = 8)
```

#### Validation group

```{r}
validation_MiOG_exploration_df <- read_csv(
  "./data/second_level_rsa/exploration_second_level/validation_MiOG_second_level.csv",
  col_types = cols(
    subgroup = col_factor(),
    subject_id = col_factor(),
    cluster = col_factor(),
    exploration_time = col_double(),
    exploration_distance = col_double(),
    capture_distance = col_double(),
  )
)
```

```{r fig.height=4, fig.width=8}
plot_second_level_RSA_exploration(validation_MiOG_exploration_df, limits = c(-0.35, 0.6), breaks = c(-0.3, 0, 0.3, 0.6), exploration_sigs = c("capture_distance"))
```

```{r}
ggsave("./output/second_level_rsa/exploration_second_level/validation_MiOG_exploration.png", height = 4, width = 8)
```


### IFG cluster

#### Discovery group

```{r}
discovery_IFG_exploration_df <- read_csv(
  "./data/second_level_rsa/exploration_second_level/discovery_IFG_second_level.csv",
  col_types = cols(
    subgroup = col_factor(),
    subject_id = col_factor(),
    cluster = col_factor(),
    exploration_time = col_double(),
    exploration_distance = col_double(),
    capture_distance = col_double(),
  )
)
```

```{r fig.height=4, fig.width=8}
plot_second_level_RSA_exploration(discovery_IFG_exploration_df, limits = c(-0.35, 0.55), breaks = c(-0.2, 0, 0.2, 0.4), exploration_sigs = c("capture_distance"))
```

```{r}
ggsave("./output/second_level_rsa/exploration_second_level/discovery_IFG_exploration.png", height = 4, width = 8)
```


#### Validation group

```{r}
validation_IFG_exploration_df <- read_csv(
  "./data/second_level_rsa/exploration_second_level/validation_IFG_second_level.csv",
  col_types = cols(
    subgroup = col_factor(),
    subject_id = col_factor(),
    cluster = col_factor(),
    exploration_time = col_double(),
    exploration_distance = col_double(),
    capture_distance = col_double(),
  )
)
```

```{r fig.height=4, fig.width=8}
plot_second_level_RSA_exploration(validation_IFG_exploration_df, limits = c(-0.35, 0.55), breaks = c(-0.2, 0, 0.2, 0.4), exploration_sigs = c("capture_distance"))
```

```{r}
ggsave("./output/second_level_rsa/exploration_second_level/validation_IFG_exploration.png", height = 4, width = 8)
```


## Partial correlation second-level RSA: Feedback History models

```{r}
plot_partial_correlation_second_level_RSA_feedback <- function(data_df, limits, breaks, feedback_sigs) {
  long_df <- data_df %>%
    pivot_longer(current_trial:previous_2_trial,
                 names_to = "model",
                 values_to = "correlation") %>%
    filter(model %in% c("recent_2_trial", "recent_3_trial")) %>% # Only using Recent-2 Trial and Recent-3 Trial models
    mutate(significant = case_when(
      model %in% feedback_sigs ~ "feedback",
      .default = "ns",
    )) %>%
  mutate(
    model = case_match(
      model,
     "recent_2_trial" ~ "Recent-2 Trial",
     "recent_3_trial" ~ "Recent-3 Trial"
    )
  ) %>%
  mutate(model = factor(
    model,
    levels = c("Recent-2 Trial", "Recent-3 Trial"))
  )
  
  long_df %>%
    ggplot(aes(x = forcats::fct_rev(model), y = correlation)) +
    geom_hline(yintercept = 0.0, linetype = "dashed") +
    stat_summary(geom = "linerange", fun.data = "mean_cl_boot", fun.args = list(B = 10000), color = '#636363', alpha = 0.3, linewidth = 13) +
    stat_summary(geom = "crossbar", fun = mean, fun.min = mean, fun.max = mean, width = 0.37, linewidth = 0.8, color = 'black') +
    geom_jitter(aes(color = significant), size = 2, alpha = 0.5, width = 0.15, height = 0) +
    coord_flip() +
    labs(x = "", y = "RSA Correlation (Z-scored)") +
    scale_color_manual(values = c('ns' = '#bdbdbd', 'feedback' = '#3182bd', 'exploration' = '#31a354')) +
    scale_y_continuous(breaks = breaks, limits = limits) +
    theme_bw() +
    global_theme +
    theme(axis.text.y = element_text(hjust = 0))
}
```


### MiOG cluster

#### Discovery group

```{r}
discovery_MiOG_partial_feedback_df <- read_csv(
  "./data/second_level_rsa/partial_feedback_history_second_level/discovery_MiOG_partial_second_level.csv",
  col_types = cols(
    subgroup = col_factor(),
    subject_id = col_factor(),
    cluster = col_factor(),
    current_trial = col_double(),
    one_back_trial = col_double(),
    two_back_trial = col_double(),
    recent_2_trial = col_double(),
    recent_3_trial = col_double(),
    previous_2_trial = col_double(),
  )
)
```


```{r fig.height=3, fig.width=6}
plot_partial_correlation_second_level_RSA_feedback(discovery_MiOG_partial_feedback_df, limits = c(-0.2, 0.4), breaks = c(-0.2, 0, 0.2, 0.4), feedback_sigs = c("recent_2_trial"))
```

```{r}
ggsave("./output/second_level_rsa/partial_feedback_history_second_level/discovery_MiOG_partial_feedback.png", height = 3, width = 6)
```

#### Validation group

```{r}
validation_MiOG_partial_feedback_df <- read_csv(
  "./data/second_level_rsa/partial_feedback_history_second_level/validation_MiOG_partial_second_level.csv",
  col_types = cols(
    subgroup = col_factor(),
    subject_id = col_factor(),
    cluster = col_factor(),
    current_trial = col_double(),
    one_back_trial = col_double(),
    two_back_trial = col_double(),
    recent_2_trial = col_double(),
    recent_3_trial = col_double(),
    previous_2_trial = col_double(),
  )
)
```

```{r fig.height=3, fig.width=6}
plot_partial_correlation_second_level_RSA_feedback(validation_MiOG_partial_feedback_df, limits = c(-0.2, 0.4), breaks = c(-0.2, 0, 0.2, 0.4), feedback_sigs = c("recent_2_trial", "recent_3_trial"))
```

```{r}
ggsave("./output/second_level_rsa/partial_feedback_history_second_level/validation_MiOG_partial_feedback.png", height = 3, width = 6)
```


### IFG cluster

#### Discovery group

```{r}
discovery_IFG_partial_feedback_df <- read_csv(
  "./data/second_level_rsa/partial_feedback_history_second_level/discovery_IFG_partial_second_level.csv",
  col_types = cols(
    subgroup = col_factor(),
    subject_id = col_factor(),
    cluster = col_factor(),
    current_trial = col_double(),
    one_back_trial = col_double(),
    two_back_trial = col_double(),
    recent_2_trial = col_double(),
    recent_3_trial = col_double(),
    previous_2_trial = col_double(),
  )
)
```

```{r fig.height=3, fig.width=6}
plot_partial_correlation_second_level_RSA_feedback(discovery_IFG_partial_feedback_df, limits = c(-0.2, 0.4), breaks = c(-0.2, 0, 0.2, 0.4), feedback_sigs = c("recent_2_trial", "recent_3_trial"))
```

```{r}
ggsave("./output/second_level_rsa/partial_feedback_history_second_level/discovery_IFG_partial_feedback.png", height = 3, width = 6)
```


#### Validation group

```{r}
validation_IFG_partial_feedback_df <- read_csv(
  "./data/second_level_rsa/partial_feedback_history_second_level/validation_IFG_partial_second_level.csv",
  col_types = cols(
    subgroup = col_factor(),
    subject_id = col_factor(),
    cluster = col_factor(),
    current_trial = col_double(),
    one_back_trial = col_double(),
    two_back_trial = col_double(),
    recent_2_trial = col_double(),
    recent_3_trial = col_double(),
    previous_2_trial = col_double(),
  )
)
```

```{r fig.height=3, fig.width=6}
plot_partial_correlation_second_level_RSA_feedback(validation_IFG_partial_feedback_df, limits = c(-0.2, 0.4), breaks = c(-0.2, 0, 0.2, 0.4), feedback_sigs = c("recent_2_trial", "recent_3_trial"))
```

```{r}
ggsave("./output/second_level_rsa/partial_feedback_history_second_level/validation_IFG_partial_feedback.png", height = 3, width = 6)
```


## Partial correlation second-level RSA: Capture Distance model

```{r}
plot_partial_correlation_second_level_RSA_capture_distance <- function(data_df, limits, breaks, sigs) {
  long_df <- data_df %>%
    pivot_longer(capture_distance__recent_2_trial:capture_distance__recent_3_trial,
                 names_to = "model",
                 values_to = "correlation") %>%
    mutate(significant = case_when(
      model %in% sigs ~ "exploration",
      .default = "ns",
    )) %>%
  mutate(
    model = case_match(
      model,
     "capture_distance__recent_2_trial" ~ "Capture Distance\n(- Recent-2 Trial)",
     "capture_distance__recent_3_trial" ~ "Capture Distance\n(- Recent-3 Trial)"
    )
  ) %>%
  mutate(model = factor(model))
    # levels = c("Recent-2 Trial", "Recent-3 Trial"))
  
  long_df %>%
    ggplot(aes(x = forcats::fct_rev(model), y = correlation)) +
    geom_hline(yintercept = 0.0, linetype = "dashed") +
    stat_summary(geom = "linerange", fun.data = "mean_cl_boot", fun.args = list(B = 10000), color = '#636363', alpha = 0.3, linewidth = 13) +
    stat_summary(geom = "crossbar", fun = mean, fun.min = mean, fun.max = mean, width = 0.37, linewidth = 0.8, color = 'black') +
    geom_jitter(aes(color = significant), size = 2, alpha = 0.5, width = 0.15, height = 0) +
    coord_flip() +
    labs(x = "", y = "RSA Correlation (Z-scored)") +
    scale_color_manual(values = c('ns' = '#bdbdbd', 'feedback' = '#3182bd', 'exploration' = '#31a354')) +
    scale_y_continuous(breaks = breaks, limits = limits) +
    theme_bw() +
    global_theme +
    theme(axis.text.y = element_text(hjust = 0))
}
```


### MiOG cluster

#### Discovery group

```{r}
discovery_MiOG_partial_capture_df <- read_csv(
  "./data/second_level_rsa/partial_capture_distance_second_level/discovery_MiOG_partial_second_level.csv",
  col_types = cols(
    subgroup = col_factor(),
    subject_id = col_factor(),
    cluster = col_factor(),
    capture_distance__recent_2_trial = col_double(),
    capture_distance__recent_3_trial = col_double(),
  )
)
```


```{r fig.height=3, fig.width=6}
plot_partial_correlation_second_level_RSA_capture_distance(discovery_MiOG_partial_capture_df, limits = c(-0.2, 0.6), breaks = c(0, 0.3, 0.6), sigs = c("capture_distance__recent_2_trial", "capture_distance__recent_3_trial"))
```


```{r}
ggsave("./output/second_level_rsa/partial_capture_distance_second_level/discovery_MiOG_partial_capture.png", height = 3, width = 6)
```


#### Validation group

```{r}
validation_MiOG_partial_capture_df <- read_csv(
  "./data/second_level_rsa/partial_capture_distance_second_level/validation_MiOG_partial_second_level.csv",
  col_types = cols(
    subgroup = col_factor(),
    subject_id = col_factor(),
    cluster = col_factor(),
    capture_distance__recent_2_trial = col_double(),
    capture_distance__recent_3_trial = col_double(),
  )
)
```

```{r fig.height=3, fig.width=6}
plot_partial_correlation_second_level_RSA_capture_distance(validation_MiOG_partial_capture_df, limits = c(-0.2, 0.6), breaks = c(0, 0.3, 0.6), sigs = c("capture_distance__recent_2_trial", "capture_distance__recent_3_trial"))
```

```{r}
ggsave("./output/second_level_rsa/partial_capture_distance_second_level/validation_MiOG_partial_capture.png", height = 3, width = 6)
```


### IFG cluster

#### Discovery group

```{r}
discovery_IFG_partial_capture_df <- read_csv(
  "./data/second_level_rsa/partial_capture_distance_second_level/discovery_IFG_partial_second_level.csv",
  col_types = cols(
    subgroup = col_factor(),
    subject_id = col_factor(),
    cluster = col_factor(),
    capture_distance__recent_2_trial = col_double(),
    capture_distance__recent_3_trial = col_double(),
  )
)
```

```{r fig.height=3, fig.width=6}
plot_partial_correlation_second_level_RSA_capture_distance(discovery_IFG_partial_capture_df, limits = c(-0.2, 0.6), breaks = c(0, 0.3, 0.6), sigs = c("capture_distance__recent_2_trial", "capture_distance__recent_3_trial"))
```

```{r}
ggsave("./output/second_level_rsa/partial_capture_distance_second_level/discovery_IFG_partial_capture.png", height = 3, width = 6)
```


#### Validation group

```{r}
validation_IFG_partial_capture_df <- read_csv(
  "./data/second_level_rsa/partial_capture_distance_second_level/validation_IFG_partial_second_level.csv",
  col_types = cols(
    subgroup = col_factor(),
    subject_id = col_factor(),
    cluster = col_factor(),
    capture_distance__recent_2_trial = col_double(),
    capture_distance__recent_3_trial = col_double(),
  )
)
```

```{r fig.height=3, fig.width=6}
plot_partial_correlation_second_level_RSA_capture_distance(validation_IFG_partial_capture_df, limits = c(-0.2, 0.6), breaks = c(0, 0.3, 0.6), sigs = c("capture_distance__recent_2_trial", "capture_distance__recent_3_trial"))
```

```{r}
ggsave("./output/second_level_rsa/partial_capture_distance_second_level/validation_IFG_partial_capture.png", height = 3, width = 6)
```


